% Place your vita below.

I am a fifth year PhD students at College of IST, PSU. My advisor is Prof. Zhenhui (Jessie) Li. My research Interest is data mining, especially mining the spatiotemporal data.




\vspace{1cm}

\centerline{Publications}

\begin{itemize}
\item \textbf{Hongjian Wang}, Huaxiu Yao, Daniel Kifer, Corina Graif, Zhenhui Li. ``Non-Stationary Model for Crime Rate Inference Using Modern Urban Data''. In \emph{IEEE Transactions on Big Data} (\textbf{TBD 2017}).
\item \textbf{Hongjian Wang}, Zhenhui Li. ``Region Representation Learning via Mobility Flow''. In \emph{Proceedings of International Conference on Information and Knowledge Management} (\textbf{CIKM 2017}).
\item \textbf{Hongjian Wang}, Zhenhui Li, Yu-Hsuan Kuo, Daniel Kifer. ``A Simple Baseline for Travel Time Estimation using Large-Scale Trip Data''. In \emph{Proceedings of the 24th ACM International Conference on Advances in Geographic Information Systems} (\textbf{SIGSPATIAL 2016}). Short paper.
\item Fei Wu, \textbf{Hongjian Wang}, Zhenhui Li. ``Interpreting traffic dynamics using ubiquitous urban data''. In \emph{Proceedings of the 24th ACM International Conference on Advances in Geographic Information Systems} (\textbf{SIGSPATIAL 2016}). Short paper.
\item \textbf{Hongjian Wang}, Daniel Kifer, Corina Graif, Zhenhui Li. ``Crime Rate Inference with Big Data''. In \emph{Proceedings of the 22nd ACM Conference on Knowledge Discovery and Data Mining} (\textbf{KDD 2016}).
\item Fei Wu, Zhenhui Li, Wang-Chien Lee, \textbf{Hongjian Wang}, Zhuojie Huang. ``Semantic Annotation of Mobility Data using Social Media''. In \emph{Proceedings of the 24th International World Wide Web Conference} (\textbf{WWW 2015}).
\item Fei Wu, \textbf{Hongjian Wang}, Zhenhui Li, Wang-Chien Lee, Zhuojie Huang. ``SemMobi: A Semantic Annotation System for Mobility Data''. In \emph{Proceedings of the 24th International World Wide Web Conference} (\textbf{WWW 2015}). System demo.
\item \textbf{Hongjian Wang}, Zhenhui Li, Wang-Chien Lee. ``PGT: Measuring Mobility Relationship Using Personal, Global and Temporal Factors''. In \emph{Proceedings of the 2014 IEEE International Conference on Data Mining} (\textbf{ICDM 2014}).
\item Ruobing Jiang, Yanmin Zhu, \textbf{Hongjian Wang}, Min Gao, Lionel M Ni. ``Compressive data retrieval with tunable accuracy in vehicular sensor networks''. In \emph{Proceedings of the 8th International Conference Wireless Algorithms, Systems, and Applications} (\textbf{WASA 2013}).
\item \textbf{Hongjian Wang}, Yamin Zhu, Qian Zhang. ``Compressive Sensing based Monitoring with Vehicular Networks''. In \emph{Proceedings of the 32nd IEEE International Conference on Computer Communications} (\textbf{INFOCOM 2013}).
\end{itemize}

